Figures and tables for paper

### 2021-10-29 analysis/04_figs-tables.Rmd
Contrast code complete

@@

```{r branding-contrasts}
# Pull the posterior draws for the organizations and compute contrasts
contrasts <- tibble(
  amnesty = draws %>% filter(level == "Amnesty International") %>% select(Gamma) %>% pull(),
  greenpeace = draws %>% filter(level == "Greenpeace") %>% select(Gamma) %>% pull(),
  oxfam = draws %>% filter(level == "Oxfam") %>% select(Gamma) %>% pull(),
  red_cross = draws %>% filter(level == "Red Cross") %>% select(Gamma) %>% pull()
) %>% 
  mutate(
    oxfam_amnesty = oxfam - amnesty,
    oxfam_greenpeace = oxfam - greenpeace,
    red_cross_amnesty = red_cross - amnesty,
    red_cross_greenpeace = red_cross - greenpeace,
  )

@@

# Reference Level = Friendly relationship with government
contrasts <- tibble(
  under_crackdown = draws %>% filter(level == "Under crackdown") %>% select(Gamma) %>% pull(),
  criticized = draws %>% filter(level == "Criticized") %>% select(Gamma) %>% pull()
  )

@@

```{r crackdown-contrasts-b}

# Pull the posterior draws for organization*government crackdown interaction

# Reference Level = Friendly relationship with government
#  contrasts <- tibble(
#    under_crackdown = draws %>% filter(level == "Under crackdown") %>% select(Gamma) %>% pull(),
#    criticized = draws %>% filter(level == "Criticized") %>% select(Gamma) %>% pull()
#    )

# Plot the contrasts
# contrasts %>%
#  pivot_longer(under_crackdown:criticized, names_to = "level", values_to = "Gamma") %>% 
#  ggplot(aes(x = Gamma, y = level)) +
#  stat_halfeye(.width = .95) +
#  geom_vline(xintercept = 0, color = "grey") +
#  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")

# Save plot
# ggsave(
#  "contrasts_hypothesis02b.png",
#  path = here::here("analysis", "output", "figures"),
#  width = 12,
#  height = 6,
#  units = "in"
# )
```

[Answer]

@@

# Reference Level = Emergency Response
contrasts <- tibble(
  environment = draws %>% filter(level == "Environment") %>% select(Gamma) %>% pull(),
  human_rights = draws %>% filter(level == "Human rights") %>% select(Gamma) %>% pull(),
  refugee_relief = draws %>% filter(level == "Refugee relief") %>% select(Gamma) %>% pull()
  )

@@

# Reference Level = Friendly relationship with government
# Reference Level = Emergency Response
# contrasts <- tibble(
#  environment = draws %>% filter(level == "Environment") %>% select(Gamma) %>% pull(),
#  human_rights = draws %>% filter(level == "Human rights") %>% select(Gamma) %>% pull(),
#  refugee_relief = draws %>% filter(level == "Refugee relief") %>% select(Gamma) %>% pull()
#  )

# Plot the contrasts
#contrasts %>%
# pivot_longer(environment:refugee_relief, names_to = "level", values_to = "Gamma") %>% 
#  ggplot(aes(x = Gamma, y = level)) +
#  stat_halfeye(.width = .95) +
#  geom_vline(xintercept = 0, color = "grey") +
#  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")

# Save plot
#ggsave(
# "contrasts_hypothesis03b.png",
#  path = here::here("analysis", "output", "figures"),
#  width = 12,
#  height = 6,
#  units = "in"
#)
```

[Answer]

@@

# Reference Level = Funded primarily by many small private donations
contrasts <- tibble(
  few_wealthy_private_donors = draws %>% filter(level == "Handful of wealthy private donors") %>% select(Gamma) %>% pull(),
  government_grants = draws %>% filter(level == "Government grants") %>% select(Gamma) %>% pull()
  )

@@

# Reference Level = Friendly relationship with government
# Reference Level = Funded primarily by many small private donations
#contrasts <- tibble(
#  few_wealthy_private_donors = draws %>% filter(level == "Handful of wealthy private donors") %>% select(Gamma) %>% pull(),
#  government_grants = draws %>% filter(level == "Government grants") %>% select(Gamma) %>% pull()
#  )

# Plot the contrasts
#contrasts %>%
#  pivot_longer(few_wealthy_private_donors:government_grants, names_to = "level", values_to = "Gamma") %>% 
#  ggplot(aes(x = Gamma, y = level)) +
#  stat_halfeye(.width = .95) +
#  geom_vline(xintercept = 0, color = "grey") +
#  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")

# Save plot
#ggsave(
#  "contrasts_hypothesis04b.png",
#  path = here::here("analysis", "output", "figures"),
#  width = 12,
#  height = 6,
#  units = "in"
#)

@@

[Answer]

@@

```{r funding-contrasts-c}
# Pull the posterior draws for funding sources*government crackdown*issue area interaction

# Reference Level = Funded primarily by many small private donations
# Reference Level = Friendly relationship with government
#contrasts <- tibble(
#  few_wealthy_private_donors = draws %>% filter(level == "Handful of wealthy private donors") %>% select(Gamma) %>% pull(),
#  government_grants = draws %>% filter(level == "Government grants") %>% select(Gamma) %>% pull()
#  )

# Plot the contrasts
#contrasts %>%
#  pivot_longer(few_wealthy_private_donors:government_grants, names_to = "level", values_to = "Gamma") %>% 
#  ggplot(aes(x = Gamma, y = level)) +
#  stat_halfeye(.width = .95) +
#  geom_vline(xintercept = 0, color = "grey") +
#  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")

# Save plot
#ggsave(
#  "contrasts_hypothesis04c.png",
#  path = here::here("analysis", "output", "figures"),
#  width = 12,
#  height = 6,
#  units = "in"
#)

@@

[Answer]

@@

# Hypothesis 5b, Organizational Practices

@@

```{r practices-contrasts-c}
# Pull the posterior draws for government crackdown*organizational practices*funding sources interaction

#contrasts <- tibble(
#  financial_transparency = draws %>% filter(level == "Financial transparency") %>% select(Gamma) %>% pull(),
#  accountability = draws %>% filter(level == "Accountability") %>% select(Gamma) %>% pull()
#  )

# Plot the contrasts
#contrasts %>%
#  pivot_longer(accountability, names_to = "level", values_to = "Gamma") %>% 
#  ggplot(aes(x = Gamma, y = level)) +
#  stat_halfeye(.width = .95) +
#  geom_vline(xintercept = 0, color = "grey") +
#  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")

# Save plot
#ggsave(
#  "contrasts_hypothesis05c.png",
#  path = here::here("analysis", "output", "figures"),
#  width = 12,
#  height = 6,
#  units = "in"
#)

@@

[Answer]

@@

```{r practices-contrasts-d}
# Pull the posterior draws for government crackdown*organizational practices*issue area interaction

#contrasts <- tibble(
#  financial_transparency = draws %>% filter(level == "Financial transparency") %>% select(Gamma) %>% pull(),
#  accountability = draws %>% filter(level == "Accountability") %>% select(Gamma) %>% pull()
#  )

# Plot the contrasts
#contrasts %>%
#  pivot_longer(accountability, names_to = "level", values_to = "Gamma") %>% 
#  ggplot(aes(x = Gamma, y = level)) +
#  stat_halfeye(.width = .95) +
#  geom_vline(xintercept = 0, color = "grey") +
#  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")

# Save plot
#ggsave(
#  "contrasts_hypothesis05d.png",
#  path = here::here("analysis", "output", "figures"),
#  width = 12,
#  height = 6,
#  units = "in"
#)

@@

[Answer]

@@

```{r practices-contrasts-e}
# Pull the posterior draws for government crackdown*organizational practices*issue area*funding sources interaction

# Reference Level = Friendly relationship with government
# Reference Level = Emergency Response
# Reference Level = Funded primarily by many small private donations

#contrasts <- tibble(
#  financial_transparency = draws %>% filter(level == "Financial transparency") %>% select(Gamma) %>% pull(),
#  accountability = draws %>% filter(level == "Accountability") %>% select(Gamma) %>% pull()
#  )

# Plot the contrasts
#contrasts %>%
#  pivot_longer(accountability, names_to = "level", values_to = "Gamma") %>% 
#  ggplot(aes(x = Gamma, y = level)) +
#  stat_halfeye(.width = .95) +
#  geom_vline(xintercept = 0, color = "grey") +
#  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")

# Save plot
#ggsave(
#  "contrasts_hypothesis05e.png",
#  path = here::here("analysis", "output", "figures"),
#  width = 12,
#  height = 6,
#  units = "in"
#)

@@

[Answer]

>>>>

```{r}
# Read in interaction draws for contrasts

intib <- read_rds(
    here::here("analysis", "output", "posterior_draws", "interactions.rds")
  )
```

@@

```{r branding-contrasts}
# Pull the posterior draws for the organizations and compute contrasts

contrasts <- tibble(
  amnesty = draws %>% filter(level == "Amnesty International") %>% select(Gamma) %>% pull(),
  greenpeace = draws %>% filter(level == "Greenpeace") %>% select(Gamma) %>% pull(),
  oxfam = draws %>% filter(level == "Oxfam") %>% select(Gamma) %>% pull(),
  red_cross = draws %>% filter(level == "Red Cross") %>% select(Gamma) %>% pull()
) %>% 
  mutate(
    oxfam_amnesty = oxfam - amnesty,
    oxfam_greenpeace = oxfam - greenpeace,
    red_cross_amnesty = red_cross - amnesty,
    red_cross_greenpeace = red_cross - greenpeace,
  )

@@

# Reference Level = Friendly relationship with government

contrasts <- tibble(
  under_crackdown = draws %>% filter(level == "Under crackdown") %>% select(Gamma) %>% pull(),
  criticized = draws %>% filter(level == "Criticized") %>% select(Gamma) %>% pull()
  )

@@

```{r crackdown-contrasts-b}
# Pull the posterior draws for organization*government crackdown interaction

# Reference Level = Friendly relationship with government

contrasts_int <- tibble(
  amnesty_criticized = intib %>% filter(i == 14) %>% select(Gamma) %>% pull(),
  greenpeace_criticized = intib %>% filter(i == 15) %>% select(Gamma) %>% pull(),
  oxfam_criticized = intib %>% filter(i == 16) %>% select(Gamma) %>% pull(),
  red_cross_criticized = intib %>% filter(i == 17)%>% select(Gamma) %>% pull(),
  amnesty_crackdown = intib %>% filter(i == 18) %>% select(Gamma) %>% pull(),
  greenpeace_crackdown = intib %>% filter(i == 19) %>% select(Gamma) %>% pull(),
  oxfam_crackdown = intib %>% filter(i == 20) %>% select(Gamma) %>% pull(),
  red_cross_crackdown = intib %>% filter(i == 21)%>% select(Gamma) %>% pull()
) %>% 
  mutate(
    oxfam_amnesty_criticized = oxfam_criticized - amnesty_criticized,
    oxfam_greenpeace_criticized = oxfam_criticized - greenpeace_criticized,
    red_cross_amnesty_criticized = red_cross_criticized - amnesty_criticized,
    red_cross_greenpeace_criticized = red_cross_criticized - greenpeace_criticized,
    oxfam_amnesty_crackdown = oxfam_crackdown - amnesty_crackdown,
    oxfam_greenpeace_crackdown = oxfam_crackdown - greenpeace_crackdown,
    red_cross_amnesty_crackdown = red_cross_crackdown - amnesty_crackdown,
    red_cross_greenpeace_crackdown = red_cross_crackdown - greenpeace_crackdown
  )
# Plot the contrasts
contrasts_int %>%
  pivot_longer(oxfam_amnesty_criticized:red_cross_greenpeace_crackdown, names_to = "level", values_to = "Gamma") %>% 
  ggplot(aes(x = Gamma, y = level)) +
  stat_halfeye(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")

# Save plot
ggsave(
  "contrasts_hypothesis02b.png",
  path = here::here("analysis", "output", "figures"),
  width = 12,
  height = 6,
  units = "in"
 )
```

These data don't support our hypothesis; the Red Cross brand has an insignificant impact on likelihood to donate compared to both Greenpeace and Amnesty. While the contrasts for Oxfam are closer to being statistically significant, the effect is working in the other direction--Greenpeace and Amnesty both induce increased likelihood to donate on behalf of donors.

@@

# Reference Level = Emergency Response

contrasts <- tibble(
  environment = draws %>% filter(level == "Environment") %>% select(Gamma) %>% pull(),
  human_rights = draws %>% filter(level == "Human rights") %>% select(Gamma) %>% pull(),
  refugee_relief = draws %>% filter(level == "Refugee relief") %>% select(Gamma) %>% pull()
  )

@@

contrasts_int <- tibble(
  criticized_environment = intib %>% filter(i == 22) %>% select(Gamma) %>% pull(),
  criticized_humanrights = intib %>% filter(i == 23) %>% select(Gamma) %>% pull(),
  criticized_refugee = intib %>% filter(i == 24) %>% select(Gamma) %>% pull(),
  crackdown_environment = intib %>% filter(i == 25) %>% select(Gamma) %>% pull(),
  crackdown_humanrights = intib %>% filter(i == 26) %>% select(Gamma) %>% pull(),
  crackdown_refugee = intib %>% filter(i == 27) %>% select(Gamma) %>% pull(),
) %>% 
  mutate(
  criticized_refugee_environment = criticized_refugee - criticized_environment,
  criticized_refugee_humanrights = criticized_refugee - criticized_humanrights,
  crackdown_refugee_environment = crackdown_refugee - crackdown_environment,
  crackdown_refugee_humanrights = crackdown_refugee - crackdown_humanrights
)
# Plot the contrasts
contrasts_int %>%
  pivot_longer(criticized_refugee_environment:crackdown_refugee_humanrights, names_to = "level", values_to = "Gamma") %>% 
  ggplot(aes(x = Gamma, y = level)) +
  stat_halfeye(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")

# Save plot
ggsave(
 "contrasts_hypothesis03b.png",
  path = here::here("analysis", "output", "figures"),
  width = 12,
  height = 6,
  units = "in"
)
```

The generated contrasts don't provides results which are statistically significant. 0 is found within all intervals.

@@

# Reference Level = Funded primarily by many small private donations

contrasts <- tibble(
  few_wealthy_private_donors = draws %>% filter(level == "Handful of wealthy private donors") %>% select(Gamma) %>% pull(),
  government_grants = draws %>% filter(level == "Government grants") %>% select(Gamma) %>% pull()
  )

@@

contrasts_int <- tibble(
  criticized_wealthydonors = intib %>% filter(i == 28) %>% select(Gamma) %>% pull(),
  criticized_grants = intib %>% filter(i == 29) %>% select(Gamma) %>% pull(),
  crackdown_wealthydonors = intib %>% filter(i == 30) %>% select(Gamma) %>% pull(),
  crackdown_grants = intib %>% filter(i == 31) %>% select(Gamma) %>% pull(),
)
# Plot the contrasts
contrasts_int %>%
  pivot_longer(criticized_wealthydonors:crackdown_grants, names_to = "level", values_to = "Gamma") %>% 
  ggplot(aes(x = Gamma, y = level)) +
  stat_halfeye(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")

# Save plot
ggsave(
  "contrasts_hypothesis04b.png",
  path = here::here("analysis", "output", "figures"),
  width = 12,
  height = 6,
  units = "in"
)

@@

The marginal posteriors for these contrasts are strange, but still tell us that the interaction between funding sources and government relationship produce no significant effects.

@@

```{r funding-contrasts-c}
# Pull the posterior draws for issue area*government crackdown*funding sources interaction

# Reference Level = Funded primarily by many small private donations
# Reference Level = Friendly relationship with government

contrasts_int <- tibble(
  emergency_crackdown_wealthydonors = intib %>% filter(i == 32) %>% select(Gamma) %>% pull(),
  emergency_crackdown_grants = intib %>% filter(i == 33) %>% select(Gamma) %>% pull(),
  environment_crackdown_wealthydonors = intib %>% filter(i == 34) %>% select(Gamma) %>% pull(),
  environment_crackdown_grants = intib %>% filter(i == 35) %>% select(Gamma) %>% pull(),
  humanrights_crackdown_wealthydonors = intib %>% filter(i == 36) %>% select(Gamma) %>% pull(),
  humanrights_crackdown_grants = intib %>% filter(i == 37) %>% select(Gamma) %>% pull(),
  refugee_crackdown_wealthydonors = intib %>% filter(i == 38) %>% select(Gamma) %>% pull(),
  refugee_crackdown_grants = intib %>% filter(i == 39) %>% select(Gamma) %>% pull(),
) %>% 
  mutate(
  emergency_humanrights_wealthydonors = emergency_crackdown_wealthydonors - humanrights_crackdown_wealthydonors ,
  emergency_environment_wealthydonors = emergency_crackdown_wealthydonors - environment_crackdown_wealthydonors,
  emergency_grants_wealthydonors = emergency_crackdown_wealthydonors - emergency_crackdown_grants,
  refugee_humanrights_wealthydonors = refugee_crackdown_wealthydonors - humanrights_crackdown_wealthydonors,
  refugee_environment_wealthydonors = refugee_crackdown_wealthydonors - environment_crackdown_wealthydonors,
  refugee_grants_wealthydonors = refugee_crackdown_grants - refugee_crackdown_wealthydonors
  )

# Plot the contrasts
contrasts_int %>%
  pivot_longer(emergency_humanrights_wealthydonors:refugee_grants_wealthydonors, names_to = "level", values_to = "Gamma") %>% 
  ggplot(aes(x = Gamma, y = level)) +
  stat_halfeye(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")

# Save plot
ggsave(
  "contrasts_hypothesis04c.png",
  path = here::here("analysis", "output", "figures"),
  width = 12,
  height = 6,
  units = "in"
)

@@

Once again, we see some interesting distributions, but no results significant enough to confirm our hypothesis.

@@

# Hypothesis 5b, Relationship with Host Government, Organizational Practices

> Donors will show increased willingness to donate to NGOs that are criticized by the government/under government crackdown when they are also financially transparent

```{r practices-contrasts-b}

# Pull the posterior draws for organizational practices*government crackdown interaction

# Reference Level = Friendly relationship with government

contrasts_int <- tibble(
  financial_transparency_criticized = intib %>% filter(i == 40) %>% select(Gamma) %>% pull(),
  financial_transparency_crackdown = intib %>% filter(i == 41) %>% select(Gamma) %>% pull(),
  )

# Plot the contrasts
contrasts_int %>%
  pivot_longer(financial_transparency_criticized:financial_transparency_crackdown, names_to = "level", values_to = "Gamma") %>% 
  ggplot(aes(x = Gamma, y = level)) +
  stat_halfeye(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")

@@

```{r practices-contrasts-c}
# Pull the posterior draws for organizational practices*funding sources*government crackdown interaction

# Reference Level = Friendly relationship with government
# Reference Level = Funded primarily by many small private donations
# All interactions include financial transparency

contrasts_int <- tibble(
  fin_smalldonors_criticized = intib %>% filter(i == 42) %>% select(Gamma) %>% pull(),
  fin_wealthydonors_criticized = intib %>% filter(i == 43) %>% select(Gamma) %>% pull(),
  fin_grants_criticized = intib %>% filter(i == 44) %>% select(Gamma) %>% pull(),
  fin_smalldonors_crackdown = intib %>% filter(i == 45) %>% select(Gamma) %>% pull(),
  fin_wealthydonors_crackdown = intib %>% filter(i == 46) %>% select(Gamma) %>% pull(),
  fin_grants_crackdown = intib %>% filter(i == 47) %>% select(Gamma) %>% pull(),
  ) %>%
  mutate(
  fin_smalldonors_wealthydonors_criticized = fin_smalldonors_criticized - fin_wealthydonors_criticized,
  fin_smalldonors_grants_criticized = fin_smalldonors_criticized - fin_grants_criticized,
  fin_smalldonors_wealthydonors_crackdown = fin_smalldonors_crackdown - fin_wealthydonors_crackdown,
  fin_smalldonors_grants_crackdown = fin_smalldonors_crackdown - fin_grants_crackdown
  )

# Plot the contrasts
contrasts_int %>%
  pivot_longer(fin_smalldonors_wealthydonors_criticized:fin_smalldonors_grants_crackdown, names_to = "level", values_to = "Gamma") %>% 
  ggplot(aes(x = Gamma, y = level)) +
  stat_halfeye(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")

# Save plot
ggsave(
  "contrasts_hypothesis05c.png",#
  path = here::here("analysis", "output", "figures"),
  width = 12,
  height = 6,
  units = "in"
)

@@

These intervals are massive; 0 is well within them, leaving us with insufficient evidence to confirm the hypothesis.

@@

```{r practices-contrasts-d}

# Pull the posterior draws for organizational practices*issue area*government crackdown interaction

# Reference Level = Friendly relationship with government
# Reference Level = Emergency Response
# All interactions include financial transparency

contrasts_int <- tibble(
  fin_emergency_criticized = intib %>% filter(i == 48) %>% select(Gamma) %>% pull(),
  fin_emergency_crackdown = intib %>% filter(i == 49) %>% select(Gamma) %>% pull(),
  fin_environment_criticized = intib %>% filter(i == 50) %>% select(Gamma) %>% pull(),
  fin_environment_crackdown = intib %>% filter(i == 51) %>% select(Gamma) %>% pull(),
  fin_humanrights_criticized = intib %>% filter(i == 52) %>% select(Gamma) %>% pull(),
  fin_humanrights_crackdown = intib %>% filter(i == 53) %>% select(Gamma) %>% pull(),
  fin_refugee_criticized = intib %>% filter(i == 54) %>% select(Gamma) %>% pull(),
  fin_refugee_crackdown = intib %>% filter(i == 55) %>% select(Gamma) %>% pull()
  ) %>%
  mutate(
  fin_emergency_environment_criticized = fin_emergency_criticized - fin_environment_criticized,
  fin_emergency_humanrights_criticized = fin_emergency_criticized - fin_humanrights_criticized,
  fin_emergency_environment_crackdown = fin_emergency_crackdown - fin_environment_crackdown,
  fin_emergency_humanright_crackdown = fin_emergency_crackdown - fin_humanrights_crackdown,
  fin_refugee_environment_criticized = fin_refugee_criticized - fin_environment_criticized,
  fin_refugee_humanright_criticized = fin_refugee_criticized - fin_humanrights_criticized,
  fin_refugee_environment_crackdown = fin_refugee_crackdown - fin_environment_crackdown,
  fin_refugee_humanright_crackdown = fin_refugee_crackdown - fin_humanrights_crackdown

# Plot the contrasts
contrasts_int %>%
  pivot_longer(fin_emergency_environment_criticized:fin_refugee_humanright_crackdown, names_to = "level", values_to = "Gamma") %>% 
  ggplot(aes(x = Gamma, y = level)) +
  stat_halfeye(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")

# Save plot
ggsave(
  "contrasts_hypothesis05d.png",
  path = here::here("analysis", "output", "figures"),
  width = 12,
  height = 6,
  units = "in"
)

@@

The contrasts don't support the hypothesis, however, there is an interesting difference between emergency_environment_crackdown and emergency_environment_criticized.

@@

```{r practices-contrasts-e}
# Pull the posterior draws for organizational practices*funding*issue area*government crackdown interaction

# Reference Level = Friendly relationship with government
# Reference Level = Emergency Response
# All interactions include small donors
# All interactions include financial transparency

contrasts_int <- tibble(
  fin_sd_emergency_criticized = intib %>% filter(i == 56) %>% select(Gamma) %>% pull(),
  fin_sd_emergency_crackdown = intib %>% filter(i == 57) %>% select(Gamma) %>% pull(),
  fin_sd_environment_criticized = intib %>% filter(i == 58) %>% select(Gamma) %>% pull(),
  fin_sd_environment_crackdown = intib %>% filter(i == 59) %>% select(Gamma) %>% pull(),
  fin_sd_humanrights_criticized = intib %>% filter(i == 60) %>% select(Gamma) %>% pull(),
  fin_sd_humanrights_crackdown = intib %>% filter(i == 61) %>% select(Gamma) %>% pull(),
  fin_sd_refugee_criticized = intib %>% filter(i == 62) %>% select(Gamma) %>% pull(),
  fin_sd_refugee_crackdown = intib %>% filter(i == 63) %>% select(Gamma) %>% pull()
  ) %>%
  mutate(
  fin_sd_emergency_environment_criticized = fin_sd_emergency_criticized - fin_sd_environment_criticized,
  fin_sd_emergency_humanrights_criticized = fin_sd_emergency_criticized - fin_sd_humanrights_criticized,
  fin_sd_emergency_environment_crackdown = fin_sd_emergency_crackdown - fin_sd_environment_crackdown,
  fin_sd_emergency_humanright_crackdown = fin_sd_emergency_crackdown - fin_sd_humanrights_crackdown,
  fin_sd_refugee_environment_criticized = fin_sd_refugee_criticized - fin_sd_environment_criticized,
  fin_sd_refugee_humanright_criticized = fin_sd_refugee_criticized - fin_sd_humanrights_criticized,
  fin_sd_refugee_environment_crackdown = fin_sd_refugee_crackdown - fin_sd_environment_crackdown,
  fin_sd_refugee_humanright_crackdown = fin_sd_refugee_crackdown - fin_sd_humanrights_crackdown

  )
# Plot the contrasts
contrasts_int %>%
  pivot_longer(fin_sd_emergency_environment_criticized:fin_sd_refugee_humanright_crackdown, names_to = "level", values_to = "Gamma") %>% 
  ggplot(aes(x = Gamma, y = level)) +
  stat_halfeye(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")

# Save plot
ggsave(
  "contrasts_hypothesis05e.png",
  path = here::here("analysis", "output", "figures"),
  width = 12,
  height = 6,
  units = "in"
)

@@

These marginal posteriors don't support our hypothesis, but again show an interesting difference between emergency_environment_criticized and emergency_environment_crackdown.

# Hypothesis 5f, Organizational Practices

# Save plot
ggsave(
  "contrasts_hypothesis05f.png",
  path = here::here("analysis", "output", "figures"),
  width = 12,
  height = 6,
  units = "in"
)
